If anything, this report illustrates that this is a complicated data set: None of the attributes are strongly correlated apart from the refractive index \texttt{RI} and the calcium content \texttt{Ca}; 6 PCA-components are needed to explain more than 90\% of the variation in the data set; and the PCA projection plot in Fig. 4.5 shows no obvious separation of the glass types apart from the 'Headlamp'-type. Clearly, any human (without a computer) will have a great deal of trouble spotting patterns in this data.

%So the question remains whether the machine learning tasks listed in section 2 are feasible. Given the above considerations, one might assume that they will not be easy. But really, it is a difficult question to answer since we know no machine learning methods at this point and thus have no real comprehension of the power of machine learning. However, as mentioned in section 2, a classification analysis on some of the dataset have been carried out with success in \cite{evett1987induction}. So our machine learning analyses to come may yet still be fruitful. 


% A classification analysis will likely give a way to pinpoint glass of type headlamp, but maybe not much else. A Regression would surely connect the Calcium percentage to RI (as the correlation suggests), but the other attributes may be difficult to predict. As for the other mentioned machine learning modeling tasks, it is very unclear what results to expect.

So the question remains whether the machine learning tasks listed in section 2 are feasible. A classification analysis will likely give a way to pinpoint glass of type headlamp, but maybe not much else. A regression would surely connect the calcium percentage to RI (as the correlation suggests), but the other attributes may be difficult to predict. As for the other machine learning tasks mentioned in Section 2, it is very unclear what results to expect. 

But really, this is a difficult question to answer since we have little knowledge about machine learning methods at this point and thus have no real comprehension of their power. Also, as mentioned in section 2, a classification analysis on some of the data set have been carried out with success in \cite{evett1987induction}. So our machine learning analyses to come may yet still be fruitful. 

